Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-03-26 manuscript.tex
first commit to GitHub

\documentclass[letterpaper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

%\documentclass[a4paper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

\makeatletter
\let\NAT@parse\undefined
\makeatother

\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{dding_template}
\input{\template/preamble/preamble_conf.tex}

\title{\LARGE \bf
Imposing a Weight Norm Constraint for Neuro–Adaptive Control
}

\author{Myeongseok Ryu$^{1}$, Jiyun Kim$^{2}$, and Kyunghwan Choi$^{1}$% <-this % stops a space
\thanks{*This work was supported by a Korea Institute for Advancement of Technology (KIAT) grant funded by the Korea Government (MOTIE) (P0020535, The Competency Development Program for Industry Specialist) \it{(Corresponding author: Kyunghwan Choi)}}% <-this % stops a space
\thanks{$^{1}$Myeongseok Ryu and Kyunghwan Choi are with the School of Mechanical and Robotics Engineering, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea {\tt\small dding\_98@gm.gist.ac.kr, khchoi@gist.ac.kr}}%
\thanks{$^{2}$Jiyun Kim is with the AI Graduate School, Gwangju Institute of Science and Technology, 61005 Gwangju, Republic of Korea 
        {\tt\small jiyun6606@gm.gist.ac.kr}}%
}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In this paper, a neuro–adaptive controller with weight norm constraints is proposed for uncertain Euler‒Lagrange systems. 
The boundedness of the weights in the neuro–adaptive controller design is important to prevent excessively large control inputs and system instability. 
To ensure the boundedness of the weights, the weight norm constraints are imposed as inequality constraints in the weight adaptation. 
The adaptation law is derived based on the constrained optimization method. 
The stability of the proposed controller is analyzed in the sense of Lyapunov, ensuring the boundedness of the tracking error and weight estimation. 
For the comparative study, two benchmark controllers and the proposed controller were evaluated through a numerical simulation of a two-link manipulator system and compared in terms of tracking performance and parameter dependency. 
The comparative study verified that the proposed controller has better tracking performance and lower parameter dependency.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  SECTION INTRODUCTION ===================================

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in\{1,\cdots,n\}}\in\R^n$ denotes a vector.
    % \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
    %     \mm A
    %     := 
    %     [a_{ij}]
    %     _{
    %         i\in[1,\cdots,n],j\in[1,\cdots ,]
    %     }\allowbreak\in\R^{n\times m}
    %     $ denotes a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix and $\mm 0_{n\times m}$ denotes the $n\times m$ zero matrix.
\end{itemize}

\section{Introduction} \label{sec:intro}

In various practical applications, Euler‒Lagrange systems generally have uncertainties due to their unknown and unmodeled dynamics.
These uncertainties degrade the control performance index.
Furthermore, if uncertainties dominate the system, they may lead to instability.
By compensating for these uncertainties, adaptive control methods have been widely used to attenuate the effects of system uncertainties \cite{Tao:2003aa,Ioannou:2006aa}.
Most conventional adaptive control methods focus on estimating unknown parameters in systems or controllers.

More recently, neuro–adaptive control approaches have been developed using neural networks (NNs) to approximate unknown system dynamics \cite{Farrell:2006aa}.
It generally uses the approximation capability of NNs with any arbitrary sigmoidal activation function \cite{Cybenko:1989aa}, which can approximate sufficiently smooth functions with minimum approximation error through ideal weights in a compact set.
This property allows the NNs to be synthesized in the controllers to approximate the unknown dynamics.
Various architectures of NNs have been proposed for neuro–adaptive control, such as single-hidden-layer NN (SHLNN) \cite{Esfandiari:2015aa,Gao:2006aa}, radial basis function NN (RBFNN) \cite{Ge:2002aa,Zhou:2023aa} and deep NN (DNN) \cite{Patil:2022aa}.
The literature has shown that NNs can improve the system's performance index and stability by approximating the unknown dynamics.

% The corresponding issue in the adaptive control is the parameter drift.
% It refers to the weight divergence during the adaptation process, while the tracking error is bounded.

% One of the common issues in neuro–adaptive control is that the boundedness of the control inputs is not guaranteed.
One of the common issues in using NNs 
\color{red}
for control compontnets
\color{black}
is that the outputs of NNs are not predictable.
This is because the input‒output relationships of the NNs are not interpretable (\ie the NNs are usually called black boxes \cite{Sheu:2020aa,Rudin:2019aa}).
\color{red}
This issue should be addressed for safety because the control input may reach the actuator's physical limitations and result in system collapse, due to the unpredictable control conponents from NNs.
\color{black}
\st{
    This issue should be addressed for safety because the unpredictable control input may reach the actuator's physical limitations and result in system collapse.
}

Most studies modify their adaptation laws to ensure the boundedness of the weights, noting that the boundedness of the NNs' output can be ensured by the boundedness of the weights.
In \cite{Zhou:2023aa,Patil:2022aa}, the projection operator is utilized to prevent weight divergence by projecting the adaptation direction on the convex set of weights.
However, in the literature, the convex set is usually selected to be as large as possible since there is no information on the ideal weights' norm.
Hence, the projection operator guarantees only the boundedness of the weights without theoretical optimality.
In addition, the $\sigma$-modification\cite{Ge:2002aa} and the $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa} are widely used to regulate the magnitude of the weights by adding a stabilizing function in the adaptation law, therby making the invariance set of the estimation error of the weights. 
The existing methods have shown their effectiveness in ensuring the boundedness of the weights via numerical simulations.
However, they lack theoretical analysis regarding the optimality of the adapted weights.

Similarly, approaches that regulate the magnitude of the weights have also been introduced in the deep learning literature.
One of the approaches is $L_2$-regularization, which adds the squared magnitudes of the weights to the objective function \cite{Wu:2020aa,Lewkowycz:2020aa}.
Then, the adaptation process attempts to reduce the magnitude of the weights, not only the original objective function.
By regulating the magnitude of the weights, the stability of the adaptation process can be enhanced, and overfitting can be prevented.
However, $L_2$-regularization also involves a trade-off between adaptation stability and the optimality of the weights.

For the theoretical analysis of weight optimality with boundedness, the constrained optimization method \cite{Nocedal:2006aa} can be utilized.
It provides the theoretical definition of optimality and the numerical methodology to solve the constrained optimization problem.
To the best of the authors’ knowledge, no prior work has utilized the constrained optimization method for the real-time weight adaptation of neuro–adaptive control satisfying weight boundedness.
Therefore, the constrained optimization method could play a pivotal role in the neuro–adaptive control design addressing the weight boundedness.

The main contributions of this study are as follows:
\begin{itemize}
    \item The neuro–adaptive control problem is reformulated into a constrained optimization problem by treating the satisfaction of the weight boundedness as inequality constraints.
    \item The adaptation law is derived based on the constrained optimization method to minimize the objective function while satisfying the weight norm constraints.
    \item The stability of the adaptation laws is analyzed via Lyapunov stability analysis, which ensures the boundedness of the tracking error and weight estimation.
\end{itemize}

The remainder of this paper is organized as follows:
Section \ref{sec: Problem Formulation} presents the target-constrained system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the adaptation law. 
Section \ref{sec:stability} examines the stability of the proposed controller.
A comparative study of the three selected controllers, including the proposed controller through numerical simulation, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper by presenting future work.

%  SECTION PROBLEM FORMULATION ============================
\section{Problem Formulation}\label{sec: Problem Formulation}

@@

Consider an uncertain Euler‒Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m\dq+ \mm G + \mm F 
    =
    \mv\tau 
    ,
    \label{eq. system dynamics 1}
\end{equation}
where $\q\in \mathbb{R}^n$ and $\mv \tau\in\R^n$ denote the generalized coordinate and the control input, respectively; $\mm M :=\mm M(\q)\in\mathbb{R}^{n\times n}$, $\mm V_m:= \mm V_m(\q,\dq)\in\mathbb{R}^{n\times n}$, and $\mm G:=\mm G(\q)\in\mathbb{R}^{n}$ denote the unknown system function matrices; and $\mm F:=\mm F(\dq)\in\mathbb{R}^{n}$ denotes the external force.
Using the user-designed matrices $\widehat{\mm M}>0,\widehat{\mm V}_m$ and $\widehat{\mm G}$, \eqref{eq. system dynamics 1} can be represented as 
\begin{equation}
    \widehat{\mm M}\ddq+\widehat{\mm V}_m\dq+\widehat{\mm G} = \mv \tau + \mv f(\q,\dq,\ddq)
    ,
    \label{eq. system dynamics 2}
\end{equation}
where $\mv f(\q,\dq,\ddq) := -(\mm M-\widehat{\mm M})\ddq-(\mm V_m-\widehat{\mm V}_m)\dq -(\mm G-\widehat{\mm G}) -\mm F$ denotes the residual unknown term.

Hence, the objective of the control design is to make $\q$ track the continuously differentiable desired trajectory $\qd:=\qd(t):\R\to \R^n$ under the unknown terms $\mv f:=\mv f(\q,\dq,\ddq)$.

@@

In this section, the neuro–adaptive controller is developed.
Section \ref{sec:ctrl dev} presents the details of the neuro–adaptive controller and the NN model.
The adaptation law based on the constrained optimization method is derived in Section \ref{sec:adap_laws} by formulating a constrained optimization problem.

\subsection{Neuro–adaptive Control Design} \label{sec:ctrl dev}

The backstepping control-based approach is utilized to generate a reference signal $\mv z^*:= -{k_q}\tilde {\q}+\dq_d$ for $\mv {z}:= \dq$, where $\tilde {\q}:= \mv {q} - \qd$ and $k_q\in\R_{>0}$.
The desired stabilizing controller can be designed as follows:
\begin{equation}
    \mv \tau^* = 
    -\widehat{\mm M}\cdot ({k_z}\tilde {\mv z})
    + 
    ( 
        -\widehat{\mm M}\tilde {\q}
        +
        \widehat{\mm V}_m{\mv z}
        +
        \widehat{\mm G}
        -
        \mv f
        +
        \widehat{\mm M} \dot {\mv z}^*
    ) 
    ,
    \label{eq. desired control}
\end{equation}
where $\tilde {\mv z}:= \mv z-\mv z^*$ and $k_z\in\R_{>0}$.
Note that the desired controller cannot be realized because of $\mv f$.

To approximate the desired controller, an NN is utilized.
\color{red}
    Even though the DNNs have a higher approximation capability than the SHLNNs \cite{Rolnick:2017aa}, here, the SHLNN is utilized for simplicity and low computational complexity.
\color{black}
The NN with a single hidden layer is represented as 
\begin{equation}
    \NN({\q_{n}};\wth):= \wV_1^\top \act(\wV_0^\top {\q_{n}})
    ,
\end{equation}
where ${\q_{n}}\in\R^{l_0+1}$ denotes the NN input vector, $\wV_i\in\R^{(l_i+1)\times l_{i+1}},\ \forall i\in\{0,1\}$ denotes the weight matrix of the $i\textsuperscript{th}$ layer and $\act:\R^{l_1}\to\R^{l_1+1}$ denotes the activation function layer.
The activation function layer consists of an elementwise nonlinear function $\sigma(\cdot)$ and an augmented $1$ to combine the bias terms in the weight matrix (\ie $\act(\mv x) = \left(\sigma(\mv x_{(1)}),\cdots, \sigma(\mv x_{(l_1)}), 1\right)^\top $).
For further simplicity, let $\wth_i:= \myvec(\wV_i)\in\R^{\Xi_i},\ \forall i\in\{0,1\}$ denotes the vectorized weights and $\wth:=(\wth_1^\top ,\wth_0^\top )^\top \in\R^{\Xi}$ denote the total weight vector, where $\Xi_i:=(l_i+1)\cdot l_{i+1},\ \forall i\in\{0,1\}$ and $\Xi:=\Xi_0+\Xi_1$ denote the number of each layer and total weights, respectively.

Using this NN, the desired controller $\mv \tau^*$ can be approximated by the ideal weight vector $\wth^*$ for a compact subset $\Omega_{NN}\in\R^{l_0+1}$ to $\epsilon$ accuracy such that $\sup_{{\q_{n}}\in\Omega_{NN}} \allowbreak \norm{\NN({\q_{n}};\wth^*) - \mv \tau^*}=\epsilon<\infty$ \cite{Cybenko:1989aa}.
The ideal weight vector $\wth^*$ is typically assumed to be bounded.
Then, using the estimated weight vector $\estwth:=(\estwth_1^\top ,\estwth_0^\top )^\top $ of $\idealwth:=({\idealwth_{1}}^{\top},{\idealwth_{0}}^{\top})^\top $ and bounded approximation error $\mv \epsilon\in\R^2$, the approximated desired controller $\mv \tau^*\approx -\NN(\q_{n};\idealwth)-\mv\epsilon$ can be estimated as follows:
\begin{equation}
    \mv \tau := -\NN({\q_{n}};\estwth)
    .
    \label{eq. control law}
\end{equation}
For further sections, let $\idealNN:=\NN({\q_{n}};\idealwth)$ and $\idealact :=\act({\idealwV_0}^{\top}{\q_{n}})$, and let $\estNN:={\NN}({\q_{n}};\estwth)$, $\estact :=\act(\estwV_0^{\top}{\q_{n}})$ and $\estact' := \pptfrac{\estact}{(\estwV_0^\top \q_{n})}$.

>>>>

\documentclass[lettersize,journal]{IEEEtran}
% code

\hyphenation{op-tical net-works semi-conduc-tor IEEE-Xplore}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{q}\kern-.125emX}}

% \usepackage{balance}
\def\pub{false} % true for publication, false for draft
\newcommand*{\template}{template}
\input{\template/preamble/preamble_conf.tex}

\newcommand*{\fe}{\mv{r}}

\begin{document}
\title{
Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints 
%Constrained Optimization-Based neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems With Input Constraints/
}

\markboth{IEEE TRANSACTIONS ON NEURAL NETWORKS AND LEARNING SYSTEMS,
~Vol.~00, No.~0, Month~2024
}%
{How to Use the IEEEtran \LaTeX \ Templates}

\maketitle

\begin{abstract}
    This study presents a constrained optimization-based neuro-adaptive controller (CoNAC) for uncertain Euler-Lagrange systems subject to weight norm and input constraints. A deep neural network (DNN) is employed to approximate the ideal stabilizing control law, compensating for lumped system uncertainties while addressing both types of constraints. The weight adaptation laws are formulated through a constrained optimization problem, ensuring first-order optimality conditions at steady state. The controller's stability is rigorously analyzed using Lyapunov theory, guaranteeing bounded tracking errors and DNN weights. Numerical simulations comparing CoNAC with three benchmark controllers demonstrate its effectiveness in tracking error regulation and satisfaction of constraints.
\end{abstract}

\begin{IEEEkeywords}
Neuro-adaptive control, constrained optimization, deep neural network, Euler-Lagrange system, input constraint.
\end{IEEEkeywords}

@@

\begin{itemize}
    \item $\otimes$ denotes the Kronecker product \cite[Definition 7.1.2]{Bernstein:2009aa}.
    \item $\mv x=[x_i]_{i\in[1,\cdots,n]}\in\R^n$ and $
        \mm A
        := 
        [a_{ij}]
        _{
            i\in[1,\cdots,n],j\in[1,\cdots ,]
        }\allowbreak\in\R^{n\times m}
        $ denote a vector and a matrix.
    \item $\myrow_i(\mm A)$ denotes the $i\textsuperscript{th}$ row of the matrix $\mm A\in\R^{n\times m}$. 
    \item $\myvec(\mm A):= [\myrow_1(\mm A^\top)  ,\cdots,\myrow_m(\mm A^\top)  ]^\top   $ for $\mm A\in\R^{n\times m}$.
    % \item $\text{col}_i(A)$ and $\myrow_j(A)$ denote the $i\textsuperscript{th}$ column and $j\textsuperscript{th}$ row of $A\in\R^{n\times m}$, respectively.
    % \item $\myvec(A):= [\text{col}_1(A)^\top  ,\cdots,\text{col}_m(A)^\top  ]^\top   $ for $A\in\R^{n\times m}$.
    \item $\lambda_\text{min}(\mm A)$ denotes the minimum eigenvalue of the matrix $\mm A\in\R^{n\times n}$.
    \item $\mm I_n$ denotes the $n\times n$ identity matrix.
\end{itemize}

%  SECTION INTRODUCTION ===================================
\section{Introduction}

\subsection{Background}

\IEEEPARstart{M}{any} engineering systems, including those in aerospace, robotics, and automotive applications, can be modeled using Euler-Lagrange systems. 
These systems are governed by dynamic equations derived from energy principles and describe the motion of mechanical systems with constraints. 
In practice, however, such systems often exhibit uncertainties due to unmodeled dynamics, parameter variations, or external disturbances. 
These uncertainties can significantly degrade control performance and, in some cases, lead to instability. 
To address these challenges, adaptive control methods have been widely employed to ensure robust performance in the presence of system uncertainties \cite{Ioannou:2006aa, Tao:2003aa}.

More recently, neuro-adaptive control approaches have been introduced to approximate unknown system dynamics or entire control laws using neural networks (NNs) \cite{Farrell:2006aa}. 
NNs are well-known for their universal approximation property, which allows them to approximate any smooth function over a compact set with minimal error. 
Various types of NNs have been utilized in neuro-adaptive control, including simpler architectures like single-hidden layer (SHL) neural networks \cite{Ge:2010aa, Yesildirek:1995aa} and radial basis function (RBF) neural networks \cite{Liu:2013ab,Ge:2002aa}, as well as more complex models like deep neural networks (DNNs) \cite{Patil:2022aa} and their variations. 
SHL and RBF NNs are often employed to approximate uncertain system dynamics or controllers due to their simplicity \cite{Esfandiari:2014aa,Esfandiari:2015aa,Yesildirek:1995aa,Gao:2006aa}, while DNNs offer greater expressive power, making them more effective for complex system approximations \cite{Rolnick:2017aa}. 
Additionally, variations of DNNs, such as long short-term memory (LSTM) networks for time-varying dynamics \cite{Liu:2013ab} and physics-informed neural networks (PINNs) for leveraging physical system knowledge \cite{Hart:2024aa}, have further extended the capabilities of neuro-adaptive control systems.

A critical aspect of neuro-adaptive control is the weight adaptation law, which governs how NN parameters are updated. 
Most studies derived these laws using Lyapunov-based methods, ensuring the boundedness of the tracking error and weight estimation error, thus maintaining system stability under uncertainty.

However, two significant challenges persist in using NNs for adaptive control. 
First, the boundedness of NN weights is not inherently guaranteed, which can result in unbounded outputs. 
When NN outputs are used directly in the control law, this may lead to excessive control inputs, violating input constraints. 
Such constraints are commonly encountered in industrial systems, where actuators are limited by physical and safety requirements in terms of amplitude, rate, or energy \cite{Esfandiari:2021aa}. 
Failing to address these constraints can degrade control performance or even destabilize the system.

Therefore, addressing these two key issues—ensuring weight boundedness and satisfying input constraints—is essential for the reliable design of neuro-adaptive controllers. 
he following section will provide a detailed review of the existing solutions to these challenges.

\subsection{Literature Review}

\subsubsection{Ensuring Weight Norm Boundedness}

A common challenge in neuro-adaptive control is maintaining the boundedness of the NN weights to ensure stability. 
In many studies, projection operators were employed to enforce upper bounds on the weight norms, ensuring that the weights do not grow unboundedly. 
For example, in \cite{Zhou:2023aa,Griffis:2023aa,Patil:2022aa}, projection operators were used to constrain the weight norms to remain below predetermined constants. 
However, these constants were often selected as large as possible due to the lack of theoretical guarantees regarding the global optimality of the weight values. 
While this approach ensured that the NN remained stable, it did not necessarily result in optimal performance.

In addition to projection operators, some studies utilized modification techniques like $\sigma$-modification \cite{Ge:2002aa} and $\epsilon$-modification \cite{Esfandiari:2015aa,Gao:2006aa}. 
These methods ensured that the NN weights remained within an invariant set by incorporating stabilizing functions into the adaptation law. 
Although these techniques were effective in ensuring boundedness and avoiding weight divergence, they similarly lacked a formal analysis of the optimality of the adapted weights, leaving room for improvement in terms of performance optimization.

\subsubsection{Satisfying Input Constraints}

The second major issue is satisfying input constraints, particularly in systems where actuators are subject to physical limitations. 
The unpredictable outputs of NNs can sometimes lead to excessively large control inputs, violating these constraints. 
This problem is exacerbated in neuro-adaptive controllers that attempt to cancel out system dynamics using conventional methods like feedback linearization or backstepping. 
In such cases, controllers may produce overly aggressive control inputs, even when the system's natural dynamics are stabilizing, leading to unnecessary saturation of the control inputs.

To address input saturation, many studies introduced auxiliary systems. 
These systems mitigated the effects of control input saturation by modifying the control strategy when saturation occurred. 
For instance, in \cite{Esfandiari:2014aa,Karason:1994aa,Esfandiari:2015aa}, auxiliary states were generated whenever input saturation was detected, and these states were incorporated into the adaptation law to adjust the NN weights accordingly. 
This approach helped the controller reduce input saturation by indirectly regulating the auxiliary states.

Alternatively, auxiliary states can also be used as feedback terms in the control law to directly compensate for the effects of input saturation constraints, as demonstrated in \cite{Arefinia:2020aa,He:2016aa,Peng:2020aa}. 
In \cite{Gao:2006aa}, the NN was used to approximate the desired control input, compensating for input saturation. 
However, these approaches typically handle input bound constraints on a per-input basis (\ie applying bounds to each scalar control variable individually), and may not account for more complex, nonlinear constraints, like input norm constraints, which are commonly found in physical systems such as robotic actuators or motor systems.

\subsubsection{Limitations of Existing Approaches and Potential of Constrained Optimization}

Although both the projection operator methods for weight norm boundedness and the auxiliary system approach for input constraints have shown effectiveness, they come with significant limitations. 
Projection operators and modification techniques do not guarantee the optimality of the adapted weights. 
Moreover, auxiliary systems typically handle only simple forms of input constraints, such as input bound constraints, limiting their ability to address more complex, nonlinear constraints like input norm constraints.

To overcome these limitations, constrained optimization offers a promising approach. 
By formulating the neuro-adaptive control problem as an optimization problem with constraints, it is possible to adapt the NN weights while minimizing an objective function (\eg tracking error) subject to both weight norm and input constraints. 
Constrained optimization provides a theoretical framework for defining optimality and presents numerical methods for finding solutions that satisfy the constraints \cite{Nocedal:2006aa}.

In existing literature, constrained optimization techniques, such as the Augmented Lagrangian Method (ALM) \cite{Evens:2021aa} and the Alternating Direction Method of Multipliers (ADMM) \cite{Wang:2019aa,Taylor:2016aa}, have been used to train NNs offline. 
These methods impose constraints to address issues like gradient vanishing in backpropagation. 
However, to the best of the authors' knowledge, no prior work has applied constrained optimization to adaptive control systems with real-time weight adaptation. 
This gap suggests that constrained optimization could be key to addressing both weight norm boundedness and input constraints in a unified, theoretically grounded framework, particularly in real-time neuro-adaptive control.

\subsection{Contributions}

The main contributions of this study are listed as follows:
\begin{itemize}
    \item A constrained optimization-based neuro-adaptive controller (CoNAC) is developed using a DNN, where input constraints and the boundedness of NN weights are formulated as inequality constraints within the adaptation process.
    \item The weight adaptation laws in CoNAC are derived using constrained optimization theory to minimize the objective function while satisfying the inequality constraints. The adaptation laws ensure convergence of the weights to the first-order optimality conditions, specifically the Karush-Kuhn-Tucker (KKT) conditions.
    \item The forward sensitivity method is applied in CoNAC to accurately calculate the gradient of the objective function. \MSRY{WILL BE DELETED}
    %, enabling more precise real-time adaptation.
\end{itemize}

\subsection{Organization}

The remainder of this paper is organized as follows. 
Section \ref{sec:Problem Formulation} presents the target system and control objective.
Section \ref{sec:ctrl design} introduces the proposed controller and the architecture of DNN in the controller. 
In Section \ref{sec:adap_laws}, the weight adaptation laws are developed.
Candidates of input constraints are presented in Section \ref{sec:appen:cstr}.
Section \ref{sec:stability} analyzes the stability of the proposed controller.
A comparative study of the four selected controllers, including the proposed controller, is reported in Section \ref{sec:sim}.
Finally, Section \ref{sec:conclusion} concludes the paper and discusses potential future work.
% The appendices provide the proof of the lemma used in the stability analysis.

%  SECTION PROBLEM FORMULATION ============================
\section{Problem Formulation}\label{sec:Problem Formulation}

@@

Consider an uncertain Euler-Lagrange system modeled as
\begin{equation}
    \mm M\ddq + \mm V_m + \mm F + \mm G + \mv\tau_d
    =
    \mysat(\mv\tau)
    \label{eq:sys1}
\end{equation}
where $\q\in \R^n$ denotes the generalized coordinate, $\mv \tau_d$ represents disturbance and $\mv\tau\in\R^n$ denotes the control input. 
The terms $\mm M:=\mm M(\q)\in\R^{n\times n}$, $\mm V_m:=\mm V_m(\q,\dq)\in\R^{n\times n}$, $\mm F:=\mm F(\dq)\in\R^{n}$ and $\mm G:=\mm G(\q)$ represent the unknown inertia matrix, Coriolis/centripetal matrix, friction terms and gravity vector
The function $\mysat(\cdot):\R^n\to\R^n$ represents the inherent physical limitations of the actuators and is defined as 
\begin{equation}
    \mysat(\mv\tau)
    :=
    \begin{cases}
        \mv\tau, 
        & 
        \text{if } \Vert\mv\tau\Vert\le \bar\tau,
        \\
        \bar\tau
        \cdot
        \tfrac{\mv\tau}{\Vert\mv\tau\Vert}, 
        & 
        \text{otherwise},
    \end{cases}
    \label{eq:sat}
\end{equation}
where $\bar\tau$ denotes the maximum norm of control input.
To account for these limitations, it is essential to incorporate physically motivated constraints into the controller design.
Appendix \ref{sec:appen:cstr} introduces candidate constraints that can be applied to ensure compliance with these physical limitations.

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} \cite{Lewis:1998aa}
    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

\begin{prop} \cite{Lewis:1998aa}
    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
    \label{prop:skew}
\end{prop}

\begin{prop}
    The disturbance $\mv\tau_d$ is bounded so that $\norm{\mv\tau_d}\le \bar\tau_d$.
    \label{prop:dis_bound}
\end{prop}

In conclusion, the control objective is to develop a neuro-adaptive controller that enables $\q$ to track a continuously differentiable desired trajectory $\qd:=\qd(t): \R \to \R^n$, compensating for the external disturbance while addressing the imposed constraints.
Considering the control input saturation function, $\qd(t)$ is supposed to satisfy the following assumption:
\begin{assum}
    The desired trajectory $\qd(t)$ is bounded so that $\norm{\qd(t)}\le \bar{q}_d$ and available to design a feasible control input in the presence of the control input saturation.
    \label{assum:feasible}
\end{assum}

@@

The architecture of the proposed CoNAC is illustrated in Fig.~\ref{fig:ctrl:diagram}, consisting of: a DNN that functions as a neuro-adaptive controller, and a weight optimizer for the DNN. 
Section \ref{sec:sub:NAC} presents the neuro-adaptive controller along with the reference generator, and Section \ref{sec:sub:NN definition} defines the DNN model. The weight optimizer will be detailed in Section \ref{sec:sub:weight optimizer}.

\begin{figure*}[!t]
    \centering
    \includegraphics[width=0.7\linewidth]{fig/Controller.drawio.png}
    % \includesvg[width=0.75\linewidth]{Controller.drawio.svg}
    \caption{Architecture of the constrained optimization-based neuro-adaptive controller (CoNAC).}
    \label{fig:ctrl:diagram}
\end{figure*}

\subsection{Neuro-Adaptive Controller Design}\label{sec:sub:NAC}

First, let us define the filtered tracking error $\fe\in\R^n$ as 
\begin{equation}
    \fe := \dot{\mv e}-\mm\Lambda \mv e
    ,
    \label{eq:err:filtered}
\end{equation}
where $\mv e := \q - \qd$ denotes the tracking error, $\dot{\mv e} := \dq - \dqd$ represents the derivative of the tracking error, and $\mm\Lambda\in\R^{n\times n}$ is a user-designed positive definite matrix.
Since \eqref{eq:err:filtered} is stable system, it implies that $\mv e$ is bounded if $\fe$ is bounded.

Using $\fe$, the system dynamics \eqref{eq:sys1} can be rewritten as
\begin{equation}
    \mm M \dot\fe
    =
    -\mm V_m \fe
    -\mm K \fe
    + \mv f
    -\mv \tau_d + \mysat(\mv\tau)
    ,
    \label{eq:sys:filtered}
\end{equation}
where $\mm K\in\R^{n\times n}$ denotes arbitrary symmetric positive definite matrix and $
    \mv f:= \mv f(\q,\dq,\dqd,\ddqd)
    =
    \mm K \fe
    +\mm M(-\ddqd+\mm\Lambda\dot{\mv e})
    +
    \mm V_m(-\dqd+\mm\Lambda\mv e)
    -
    \mm F
    -
    \mm G
    \in\R^n
$ denotes the lumped system uncertainty.

Consider the Lyapunov function $V_1:= \tfrac{1}{2}\fe^\top \mm M\fe$. 
Invoking Property \ref{prop:skew}, the time derivative of $V_1$ is
\begin{equation}
    \begin{aligned}
        \ddtt{V}_1
        =&
        \fe^\top \mm M (
            -\mm V_m \fe -\mm K \fe + \mv f
            -\mv \tau_d + \mysat(\mv\tau)
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top \dot{\mm M}\fe
        \\
        =&
        -
        \fe^\top \mm K \fe 
        +
        \fe^\top (
            \mv f+\mysat(\mv\tau)
            -\mv \tau_d
        )
        \\
        &
        +
        \tfrac{1}{2}
        \fe^\top(\dot{\mm M}- 2\mm V_m)\fe
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mv f+\mysat(\mv \tau))
        \\
        \le&
        -\lambda_\text{min}(\mm K)\norm{\fe}^2
        +
        \bar\tau_d\norm{\fe}
        +
        \fe^\top (\mysat(\mv\tau)-\mv\tau^*)
        ,
    \end{aligned}
    \label{eq:lya1:dot1}
\end{equation}
where $\mv\tau^*:= -\mv f$ is the ideal control input whose maximum norm is $\bar\tau$ according to Assumption \ref{assum:feasible} and \eqref{eq:sat}. 
Therefore, one can conclude that $\fe$ is exponentially stable so that $\lim_{t\to\infty}\norm{\fe}=\tfrac{\bar\tau_d}{\lambda_\text{min}(\mm K)}$, if $\mv \tau=-\mv\tau^*$ can be realized.
However, $\mv \tau^*$ is not available in practice, since $\mv f$ is unknown.

To overcome this issue, a DNN is employed to approximate $\mv\tau^*$.
Let $\NN:=\NN(\q_{NN};\wth): \R^{l}\times\R^{\Xi}\to\R^{n}$ represent the DNN, where $\q_{NN}\in\R^{l}$ is the DNN input vector, and $\wth\in\R^{\Xi}$ is the vector of trainable weights.
The architecture of $\NN(\q_{NN};\wth)$ will be defined in Section \ref{eq:DNN:architecture}.
According to the universal approximation theorem for DNNs \cite{Kidger:2020aa}, $\NN(\q_{NN};\wth)$ can approximate a nonlinear function $\mv g(\cdot)$ with an ideal weight vector $\idealwth$ on a compact subset $\Omega_{NN}\in\R^{l}$ to $\mv\epsilon$-accuracy, such that $\sup_{\q_{NN}\in\Omega_{NN}}\norm{ \NN(\q_{NN};\idealwth) - \mv g(\cdot)} = \mv\epsilon < \infty$.
Furthermore, the theorem states that the norm of $\idealwth$ is bounded, \ie $\norm{\idealwth}\le \bar\wth<\infty$.
In this study, $\idealwth$ is defined as a local optimal point, rather than a global optimal point.

In conclusion, the ideal control law $\mv\tau^*$ is expressed by the DNN approximation with the ideal weight vector $\idealNN:=\NN(\q_{NN};\idealwth)$ as follows:
\begin{align}
    \mv\tau^*=& \idealNN+\mv\epsilon,
    \label{eq:control:ideal}
\end{align}
which is estimated online by
\begin{align}
    \mv\tau =& \estNN,
    \label{eq:control:est}
\end{align}
where $\hat\NN:=\NN(\q_{NN};\estwth)$, and  $\estwth$ is the estimated weight vector for $\idealwth$.
